Multisensor Architecture for an Intersection Management System

### 2015-03-20 ch2-mdf_ims.tex
Updated bibliography and redesigned figure 2.5 to a table

@@

@@

%\begin{figure}[ht!]
%\centering
%\includegraphics[scale=0.275]{fig/2/fusionAlg.png}
%\caption{Fusion algorithms based on level of fusion. (from \cite{Luo2011})}
%\label{fusionAlgs}
%\end{figure}

>>>>

\begin{table}
\centering
\begin{tabular}{c c}
Category & Data Fusion Model \\

\hline
\multirow{2}{*}{Abstract Model} & Waterfall Model \cite{Harris1998} \\
& Boyd Loop \cite{Boyd1987} \\
\hline
\multirow{3}{*}{Generic Architecture} & JDL Model \cite{White1991} \\
& Multisensor Fusion Integration Model \cite{Luo1989} \\
& Omnibus model \cite{Bedworth2000} \\
\hline
\multirow{3}{*}{Rigid Architecture} & LAAS Architecture \cite{Alami1998} \\
& DFuse Architecture \cite{Kumar2003} \\
& Time-triggered Model \cite{Elmenreich2001} \\
\hline
\end{tabular}
\caption{Classification of data fusion models.}
\end{table}

@@

Luo in \cite{Luo2011} propose a classification for fusion algorithms based on the level of fusion. Low-level fusion refers to the merge of raw data or signals, mid-level fusion refers to the fusion of features and High-level fusion refers to the process of fuse decisions.

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.175]{fig/2/ims_graph.png}
\caption{Fusion algorithms based on level of fusion. (from \cite{Luo2011})}
\label{fusionAlgs}
\end{figure}
